Predictors of frog survival following translocations - analyses

### 2022-03-16 code/translocation_survival_exploratory.Rmd
Minor edit to add reference for color palette

# define color palette
```{r define-color-palette}
palette_cbb <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

>>>>

# define color palette (palette_OkabeIto_black)
```{r define-color-palette}
palette_cbb <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```
